Active Learning for SAT Solver Benchmarking

### 2023-01-12 paper/paper.tex
Fix R3 comment on Future Work

On a more general note, one can apply our evaluation framework to arbitrary $\mathcal{NP}$-complete problems, as all discussed active-learning methods are problem-agnostic.
%JB: TODO: clarify that our approach works for any computation-intensive problem, not only NP-complete (comment of Reviewer 3)
These problems share most of the relevant properties of SAT solving, i.e., there are established instance features, a complete benchmark run takes a considerable amount of time, and solver benchmarking traditionally requires expert knowledge to hand-select instances.

>>>>

On a more general note, one can apply our evaluation framework to arbitrary computation-intensive problems, e.g., other $\mathcal{NP}$-complete problems than SAT, as all discussed active-learning methods are problem-agnostic.
These problems share most of the relevant properties of SAT solving, i.e., there are established instance features, a complete benchmark run takes a considerable amount of time, and solver benchmarking traditionally requires expert knowledge to hand-select instances.
